### 2019-11-07 report/paper.tex
update

@@

\subsection{Discussion}
Strengths and weakness in your method.

Maybe we can talk about the methods we also tried but didn't work/didn't use for the final solution here(?)

Strengths
Schnell
Accuracy für Waldo

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

>>>>

When comparing the performance of the HOG/HOV \& SVM approach to only using the HOG feature descriptor in \autoref{tab:class-iou}
one can verify the relevance of our extension to the HOG feature descriptor. As highlighted, the mean IoU (Intersection over Union) 
of ground truth bounding boxes to detection results is significantly improved when providing additional value information via the HOV descriptor, 
compared to only using the HOV descriptor.
However the greater IoU comes at the cost of additional computational expense, as highlighted by the mean computation time of each method.

@@

\subsection{Discussion}
% Strengths and weakness in your method.

% Maybe we can talk about the methods we also tried but didn't work/didn't use for the final solution here(?)

% Strengths
% Schnell
% Accuracy für Waldo

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& A0207441N & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
